---
title: "Time and Project Management"
format: html

---

## Risk Matrix

### Paper 1 - RCT study

+---------+--------------------------------+-------------------------------------------------------------------------------+-------------+--------+----------------------------------------------------------------------------------------------------------------------------------------------------+
| Risk ID | Risk name                      | Risk description                                                              | Probability | Impact | Risk remediation plan (prevent or minimize)                                                                                                        |
+=========+================================+===============================================================================+=============+========+====================================================================================================================================================+
| 1       | Delayed data-sharing agreement | Data-sharing agreement with SDU may be delayed, which could prolong analysis. | Medium      | Medium | Follow up frequently with SDU, clarify unresolved issues early, and work on parallel tasks to minimize delays. Keep Søren updated with Cc. mails.  |
+---------+--------------------------------+-------------------------------------------------------------------------------+-------------+--------+----------------------------------------------------------------------------------------------------------------------------------------------------+
| 2       | Participant withdrawal         | Participant dropout may reduce sample size and weaken statistical power.      | Low         | Medium | Assess whether statistical analyses can be adapted to smaller samples without compromising validity.                                               |
+---------+--------------------------------+-------------------------------------------------------------------------------+-------------+--------+----------------------------------------------------------------------------------------------------------------------------------------------------+
| 3       | Additional trial site          | Adding a new trial site may extend analysis timelines.                        | Low         | Medium | Ensure that any added trial site has a large patient uptake to minimize added time.                                                                |
+---------+--------------------------------+-------------------------------------------------------------------------------+-------------+--------+----------------------------------------------------------------------------------------------------------------------------------------------------+

------------------------------------------------------------------------

### Paper 2 - Register based study

+---------+---------------------------+---------------------------------------------------------------------+-------------+--------+---------------------------------------------------------------------------------------------------+
| Risk ID | Risk name                 | Risk description                                                    | Probability | Impact | Risk remediation plan (prevent or minimize)                                                       |
+=========+===========================+=====================================================================+=============+========+===================================================================================================+
| 4       | Delay in integrating data | Integrating HiM cohort data with Statistics Denmark may be delayed. | Medium      | Medium | Create a fake dataset that I can do my statistical analysis on. \                                 |
|         |                           |                                                                     |             |        | Start analysis that can be done meanwhile.\                                                       |
|         |                           |                                                                     |             |        | Maintain close coordination with the integration team.                                            |
+---------+---------------------------+---------------------------------------------------------------------+-------------+--------+---------------------------------------------------------------------------------------------------+
| 5       | Insufficient data type    | Data may not support longitudinal analysis of physical activity.    | High        | High   | Shift to a descriptive or cross-sectional design and highlight what insights can still be gained. |
+---------+---------------------------+---------------------------------------------------------------------+-------------+--------+---------------------------------------------------------------------------------------------------+

------------------------------------------------------------------------

### Paper 3 - Qualitiative study

+---------+---------------------+------------------------------------------------------------------------+-------------+--------+----------------------------------------------------------------------------------------------------------------------------------+
| Risk ID | Risk name           | Risk description                                                       | Probability | Impact | Risk remediation plan (prevent or minimize)                                                                                      |
+=========+=====================+========================================================================+=============+========+==================================================================================================================================+
| 6       | Limited preparation | Limited time for preparation may delay data collection to summer 2026. | Medium      | Medium | Move data collection to summer 2026 if needed and use the extra months to complete Paper 2 earlier or start analyses on paper 1. |
+---------+---------------------+------------------------------------------------------------------------+-------------+--------+----------------------------------------------------------------------------------------------------------------------------------+

### Relationships & Personal Considerations

+---------+----------------------------+--------------------------------------------------------------------------------------+-------------+--------+-------------------------------------------------------------------------------------------------------------------------------------------------------+
| Risk ID | Risk name                  | Risk description                                                                     | Probability | Impact | Risk remediation plan (prevent or minimize)                                                                                                           |
+=========+============================+======================================================================================+=============+========+=======================================================================================================================================================+
| 7       | Family–work imbalance      | Timeline delays may affect family balance and increase workload at home.             | High        | High   | Talk openly with supervisor, set work boundaries, and find shared solutions with my wife.\                                                            |
|         |                            |                                                                                      |             |        | Stick to predefined working hours and work a maximum of 90 min. in the evening.                                                                       |
+---------+----------------------------+--------------------------------------------------------------------------------------+-------------+--------+-------------------------------------------------------------------------------------------------------------------------------------------------------+
| 8       | Australia stay challenges  | Practical challenges may make the Australia research stay unfeasible for the family. | High        | Low    | If family arrangements fail, explore shorter or alternative international stays with less impact on family life.                                      |
+---------+----------------------------+--------------------------------------------------------------------------------------+-------------+--------+-------------------------------------------------------------------------------------------------------------------------------------------------------+
| 9       | Changing project direction | Supervisor’s change in project direction may increase workload.                      | Medium      | Medium | Discuss implications openly, assess alignment with PhD aims, and negotiate workload. Supervisor is reasonable and responsive to well-argued concerns. |
+---------+----------------------------+--------------------------------------------------------------------------------------+-------------+--------+-------------------------------------------------------------------------------------------------------------------------------------------------------+

## Plottet risks and visuals

```{r}
#| label: risk-matrix
#| fig-cap: "Probability–Impact Matrix for project risks."
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 6

library(ggplot2)
library(ggrepel)
library(dplyr)
library(tibble)

# ------------------------------------------------------------------
# 1. Define the risks (ID + name + probability + impact)
# ------------------------------------------------------------------

risks <- tribble(
  ~RiskID, ~RiskName, ~Probability, ~Impact,
  "1", "Delayed data-sharing agreement", "Medium", "Medium",
  "2", "Participant withdrawal", "Low", "Medium",
  "3", "Additional trial site", "Low", "Medium",
  "4", "Delay in integrating data", "Medium", "Medium",
  "5", "Insufficient data type", "High", "High",
  "6", "Limited preparation", "Medium", "Medium"
)

# ------------------------------------------------------------------
# 2. Convert Probability & Impact to numeric positions (Low–Medium–High)
# ------------------------------------------------------------------

level_map <- c("Low" = 1, "Medium" = 2, "High" = 3)

risks <- risks %>%
  mutate(
    Prob_num = level_map[Probability],
    Impact_num = level_map[Impact]
  )

# Add jitter so labels do not overlap
set.seed(42)
risks <- risks %>%
  mutate(
    Prob_jit = Prob_num + runif(n(), -0.1, 0.1),
    Impact_jit = Impact_num + runif(n(), -0.1, 0.1)
  )

# ------------------------------------------------------------------
# 3. Background colors for the 3×3 grid (same structure as your matrix)
# ------------------------------------------------------------------

bg_colors <- data.frame(
  xmin = rep(c(0.5, 1.5, 2.5), each = 3),
  xmax = rep(c(1.5, 2.5, 3.5), each = 3),
  ymin = rep(c(0.5, 1.5, 2.5), times = 3),
  ymax = rep(c(1.5, 2.5, 3.5), times = 3),
  fill = rep(
    c("#f2f2f2", "#e8f5e9", "#dcedc8",
      "#fff9c4", "#ffe0b2", "#ffccbc",
      "#f2f2f2", "#e8f5e9", "#dcedc8"), 1
  )
)

# ------------------------------------------------------------------
# 4. Plot
# ------------------------------------------------------------------

ggplot() +
  geom_rect(
    data = bg_colors,
    aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill),
    color = "grey80"
  ) +
  scale_fill_identity() +
  
  geom_point(
    data = risks,
    aes(x = Prob_jit, y = Impact_jit),
    size = 3,
    color = "#1b5e20"
  ) +
  
  geom_label_repel(
    data = risks,
    aes(x = Prob_jit, y = Impact_jit, label = paste0("Risk ", RiskID, ": ", RiskName)),
    size = 3.3,
    color = "black",
    fill = "white",
    box.padding = 0.3,
    label.size = 0.2,
    segment.color = "grey60",
    max.overlaps = Inf
  ) +
  
  scale_x_continuous(
    breaks = 1:3,
    labels = c("Low", "Medium", "High"),
    limits = c(0.5, 3.5)
  ) +
  scale_y_continuous(
    breaks = 1:3,
    labels = c("Low", "Medium", "High"),
    limits = c(0.5, 3.5)
  ) +
  
  labs(
    x = "Probability of occurrence",
    y = "Impact on project",
    title = "Risk Probability–Impact Matrix"
  ) +
  
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 14)
  )
```

## Plottet risks and visuals for personal and relational risks

```{r}
#| label: risk-matrix-relationships
#| fig-cap: "Probability–Impact Matrix for personal and relational risks."
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 6

library(ggplot2)
library(ggrepel)
library(dplyr)
library(tibble)

# -------------------------------------------------------------
# 1. Define risks
# -------------------------------------------------------------

risks_rel <- tribble(
  ~RiskID, ~RiskName, ~Probability, ~Impact,
  "7", "Family–work imbalance", "High", "High",
  "8", "Australia stay challenges", "High", "Low",
  "9", "Changing project direction", "Medium", "Medium"
)

# -------------------------------------------------------------
# 2. Convert categorical levels to numeric scale
# -------------------------------------------------------------

level_map <- c("Low" = 1, "Medium" = 2, "High" = 3)

risks_rel <- risks_rel %>%
  mutate(
    Prob_num = level_map[Probability],
    Impact_num = level_map[Impact]
  )

# Add jitter to avoid label overlap
set.seed(1234)
risks_rel <- risks_rel %>%
  mutate(
    Prob_jit = Prob_num + runif(n(), -0.1, 0.1),
    Impact_jit = Impact_num + runif(n(), -0.1, 0.1)
  )

# -------------------------------------------------------------
# 3. Background color grid (same as previous matrices)
# -------------------------------------------------------------

bg_colors <- data.frame(
  xmin = rep(c(0.5, 1.5, 2.5), each = 3),
  xmax = rep(c(1.5, 2.5, 3.5), each = 3),
  ymin = rep(c(0.5, 1.5, 2.5), times = 3),
  ymax = rep(c(1.5, 2.5, 3.5), times = 3),
  fill = rep(
    c("#f2f2f2", "#e8f5e9", "#dcedc8",
      "#fff9c4", "#ffe0b2", "#ffccbc",
      "#f2f2f2", "#e8f5e9", "#dcedc8"), 1
  )
)

# -------------------------------------------------------------
# 4. Plot
# -------------------------------------------------------------

ggplot() +
  geom_rect(
    data = bg_colors,
    aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = fill),
    color = "grey80"
  ) +
  scale_fill_identity() +
  
  geom_point(
    data = risks_rel,
    aes(x = Prob_jit, y = Impact_jit),
    size = 3,
    color = "#1b5e20"
  ) +
  
  geom_label_repel(
    data = risks_rel,
    aes(
      x = Prob_jit,
      y = Impact_jit,
      label = paste0("Risk ", RiskID, ": ", RiskName)
    ),
    size = 3.3,
    color = "black",
    fill = "white",
    box.padding = 0.3,
    label.size = 0.2,
    segment.color = "grey60",
    max.overlaps = Inf
  ) +
  
  scale_x_continuous(
    breaks = 1:3,
    labels = c("Low", "Medium", "High"),
    limits = c(0.5, 3.5)
  ) +
  scale_y_continuous(
    breaks = 1:3,
    labels = c("Low", "Medium", "High"),
    limits = c(0.5, 3.5)
  ) +
  
  labs(
    x = "Probability of occurrence",
    y = "Impact on project",
    title = "Relationships & Personal Considerations: Probability–Impact Matrix"
  ) +
  
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(),
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 14)
  )
```
